Brief Announcement: Tight Bounds for Online Balanced Repartitioning

### 2020-03-26 paper/paper.tex
Future
Table sketch

@@

>>>>

\usepackage{balance}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage{amsthm,amsmath,amssymb,array,colortbl,graphicx,multirow}
\usepackage{comment}
\usepackage{balance}
\usepackage{tikz}
\usepackage{amsmath}
\usetikzlibrary{patterns} %
\usepackage{algorithm}
\usepackage[font={footnotesize}]{subcaption}
\usepackage[font={footnotesize}]{caption}
\usepackage{breakcites}
\usepackage{booktabs}
\usepackage{diagbox}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{cleveref}
\usepackage{enumitem}

@@

  \section{Final}

  \begin{table*}
    \centering
    \renewcommand{\arraystretch}{1.5}
      \begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
      \rowcolor{gray!50}
      \textbf{Clusters/capacity} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
        \textbf{$k=2$}& 3~\cite{repartition-disc} & 3~(\S 9.3) \\ 
        \rowcolor{gray!25}
        \textbf{$k=3$}&  $1357\cdot \ell - 245 = \Omega(\ell)$ (\S 9.3)& $O(k \cdot \ell)$~\cite{repartition-disc}\\
        \textbf{$\ell=2$}&  $2k-1$ (\S 9.3)& $O(k^2)$~\cite{repartition-disc}\\
        \rowcolor{gray!25}
        general $k$ and $\ell$& $\Omega(k\cdot \ell)$ (\S 9.3)&$O(k^2 \cdot \ell^2)$~\cite{repartition-disc} \\
      \end{tabular}
                  \caption{Overview of the results. Most specific cases are tight. The general case still has a significant gap between the lower bound and the upper bound.
                    }
    \label{tab:overview}
    \vspace{-7mm}
  \end{table*}

  Table with summary of all results. Tight for k=2, asymptotically tight for k=3, and a difference in general lk.

  No bypassing model: reserach.
